Appendix 1: sdmTMB statistical model description

### 2021-12-22 doc/appendix-model.Rmd
Change distr formatting

## [Binomial](https://kaskr.github.io/adcomp/group__R__style__distribution.html#gaee11f805f02bc1febc6d7bf0487671be)

@@

@@

## [Beta](https://kaskr.github.io/adcomp/group__R__style__distribution.html#ga5324c83759d5211c7c2fbbad37fa8e59)

@@

@@

## [Gamma](https://kaskr.github.io/adcomp/group__R__style__distribution.html#gab0e2205710a698ad6a0ed39e0652c9a3)

@@

@@

## [Gaussian](https://kaskr.github.io/adcomp/dnorm_8hpp.html)

@@

## [Lognormal](https://github.com/pbs-assess/sdmTMB/blob/18a39eabc111e2179fa589f942c8820d87ad10df/src/utils.h#L47-L54)

@@

@@

## [Negative Binomial 1 (NB1)](https://github.com/pbs-assess/sdmTMB/blob/18a39eabc111e2179fa589f942c8820d87ad10df/src/sdmTMB.cpp#L577-L582)

@@

@@

## [Negative Binomial 2 (NB2)](https://kaskr.github.io/adcomp/group__R__style__distribution.html#ga76266c19046e04b651fce93aa0810351)

@@

@@

## [Poisson](https://kaskr.github.io/adcomp/group__R__style__distribution.html#gaa1ed15503e1441a381102a8c4c9baaf1)

@@

@@

## [Student-t](https://github.com/pbs-assess/sdmTMB/blob/18a39eabc111e2179fa589f942c8820d87ad10df/src/utils.h#L37-L45)

@@

@@

## [Tweedie](https://kaskr.github.io/adcomp/group__R__style__distribution.html#ga262f3c2d1cf36f322a62d902a608aae0)

@@

The [source code](https://kaskr.github.io/adcomp/tweedie_8cpp_source.html) is implemented as in the [cplm](https://CRAN.R-project.org/package=cplm) package [@zhang2013a] and is based on @dunn2005.

>>>>

## Binomial

@@

Code defined [within TMB](https://kaskr.github.io/adcomp/group__R__style__distribution.html#gaee11f805f02bc1febc6d7bf0487671be).

@@

## Beta

@@

Code defined [within TMB](https://kaskr.github.io/adcomp/group__R__style__distribution.html#ga5324c83759d5211c7c2fbbad37fa8e59).

@@

## Gamma

@@

Code defined [within TMB](https://kaskr.github.io/adcomp/group__R__style__distribution.html#gab0e2205710a698ad6a0ed39e0652c9a3).

@@

## Gaussian

@@

Code defined [within TMB](https://kaskr.github.io/adcomp/dnorm_8hpp.html).

## Lognormal

@@

Code defined [within sdmTMB](https://github.com/pbs-assess/sdmTMB/blob/18a39eabc111e2179fa589f942c8820d87ad10df/src/utils.h#L47-L54) based on the TMB `dnorm()` normal density.

@@

## Negative Binomial 1 (NB1)

@@

Code defined [within sdmTMB](https://github.com/pbs-assess/sdmTMB/blob/18a39eabc111e2179fa589f942c8820d87ad10df/src/sdmTMB.cpp#L577-L582) based on NB2 and borrowed from glmmTMB.

@@

## Negative Binomial 2 (NB2)

@@

Code defined [within TMB](https://kaskr.github.io/adcomp/group__R__style__distribution.html#ga76266c19046e04b651fce93aa0810351).

@@

## Poisson

@@

Code defined [within TMB](https://kaskr.github.io/adcomp/group__R__style__distribution.html#gaa1ed15503e1441a381102a8c4c9baaf1).

@@

## Student-t

@@

Code defined [within sdmTMB](https://github.com/pbs-assess/sdmTMB/blob/18a39eabc111e2179fa589f942c8820d87ad10df/src/utils.h#L37-L45) based on the `dt()` distribution in TMB.

@@

## Tweedie

@@

The [source code](https://kaskr.github.io/adcomp/tweedie_8cpp_source.html) is implemented as in the [cplm](https://CRAN.R-project.org/package=cplm) package [@zhang2013a] and is based on @dunn2005. The TMB version is defined [here](https://kaskr.github.io/adcomp/group__R__style__distribution.html#ga262f3c2d1cf36f322a62d902a608aae0).
